---
title: "p8105_hw5_zz2780"
author: "Lydia Zhang"
date: "2022-11-15"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

Problem 1
Import the data
```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```
Tidy the data
```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```
Graph

"This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way."
```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```
Problem 2

Load the data from Github Repo
```{r}
data2<-read.csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")
```

The raw data contains each homicide's case number, reported date, victims' name, race, age, gender, the city and state of homicide, its specific longitude and latitude, and the disposition.

The code below created variables city_state, grouped by cities and summarized the number of total or unsolved homicides within each city.
```{r}
data2_summary<-data2%>%
  mutate(
    city_state=paste(city, state, sep=", "))%>%
  group_by(city_state)%>%
 summarize(total=n(),
           unsolved=sum(disposition!="Closed by arrest"))

data2_summary
```
I subset the data summary to only city of Baltimore, ran the proportional test, and stored the prop test result as dataframe bal.test.
```{r}
baltimore<-data2_summary%>%
  subset(city_state=="Baltimore, MD")
bal.test<-broom::tidy(prop.test(baltimore$unsolved, baltimore$total))
```

I ran prop.test on every city, stored the test results in new variable test, and extract estimates and 95%CI from the test variable. Finally I deleted test variable for tidy purpose.
```{r}
data2_prop_test<-data2_summary%>%
  mutate(
    test=purrr::map2(unsolved, total, prop.test),
    estimate=map_dbl(test,~.x[["estimate"]]),
    ci_lower=map_dbl(test,~.x[["conf.int"]][1]),
    ci_upper=map_dbl(test,~.x[["conf.int"]][2])
    )%>%
  select(-test)

data2_prop_test
```
The bar plot below shows, in descending order, the proportion of unsolved homicides in each city as well as each 95% CI.
```{r}
ggplot(data2_prop_test, aes(x =reorder(city_state, desc(estimate)), y = estimate)) +
  geom_bar(stat="identity")+
  geom_errorbar(width=.1, aes(ymin=ci_lower,ymax=ci_upper),position=position_dodge(width=0.5))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(x="City, State", y = "Proportion of Unsolved Homicide",title="Proportion of Unsolved Homicide in Each City")
```





